---
title: "Project 1: Getting Started"
subtitle: "MKTG 411 Marketing Analytics"
output: 
  ioslides_presentation:
    widescreen: true
    css: ../style.css
---

## Load Libraries 

Let's load packages and import the data. Note that we are only demonstrating what we have already done to import the data from the database and using the Qualtrics API.

```{r echo = TRUE, results = 'hide', message=FALSE}
# Load packages.
library(RPostgres)
library(tidyverse)
library(dbplyr)
library(DBI)
library(qualtRics)
```

## Setup Database Connection

```{r}
con <- dbConnect(
  RPostgres::Postgres(),
  dbname = "analyticsdb",
  host = "analyticsdb.c5i8use80ktf.us-east-2.rds.amazonaws.com",
  port = 5432,
  user = "quantmktg",
  password = rstudioapi::askForPassword("Database password")
)

dbListTables(con)
```

## Load Data from Database

```{r}
# Import online_transactions.
online_transactions <- tbl(con, "online_transactions") |>
  collect()

# Import online_revenue.
online_revenue <- tbl(con, "online_revenue") |>
  collect()

# Import customer_data.
customer_data <- tbl(con, "customer_data") |>
  collect()

# Import store_revenue.
store_revenue <- tbl(con, "store_revenue") |>
  collect()

# Import store_transactions.
store_transactions <- tbl(con, "store_transactions") |>
  collect()

# Disconnect from the database.
dbDisconnect(con)
```

## Qualtrics API Connection

```{r}
# Set qualtrics API credentials
qualtRics::qualtrics_api_credentials(
  api_key = "Ir2JDPvhOjSmMIpWo8bwVUAbvPs6uwGqIKipAuo6", 
  base_url = "sjc1.qualtrics.com"
)

# Connect to API.
survey_data <- fetch_survey("SV_0rn3HbR4AEc1BUG")
```

## Save Data Locally

```{r}
# Write data locally.
write_csv(online_transactions, "online_transactions.csv")
write_csv(online_revenue, "online_revenue.csv")
write_csv(customer_data, "customer_data.csv")
write_csv(store_revenue, "store_revenue.csv")
write_csv(store_transactions, "store_transactions.csv")
write_csv(survey_data, "survey_data.csv")
```

## Preventing Future Connections

Use `#| eval: false` in the previous chunks to avoid connecting to the database and API when rendering your Quarto document.

## Import Your Data

```{r}
# Import data.
customer_data <- read_csv("customer_data.csv")
store_transactions <- read_csv("store_transactions.csv")
store_revenue <- read_csv("store_revenue.csv")
online_transactions <- read_csv("online_transactions.csv")
online_revenue <- read_csv("online_revenue.csv")
survey_data <- read_csv("survey_data.csv")
```

## Your Turn!

Answer the rest of the questions described in the project document. Ethan and I are here to answer questions.